Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-05-07 ms.tex
minor clean-up of section introducing two-component model

The primary FDS99 analysis considered the grain properties, for example the
emissivity power law indices $\beta$, to be constant over the sky, and 
performed a correlation slope analysis to constrain these parameters with
FIRAS and DIRBE observations. A DIRBE 240$\mu$m/100$\mu$m ratio was used
to account for temperature variation at $\sim$1.3$^{\circ}$ resolution. In this
work we seek to apply FDS99-like emission models to the \PLANCK~data set, which
offers a dramatic enhancement in angular resolution relative to the FIRAS 
spectra. The \PLANCK~data allow us to derive a temperature correction at 
near-\IRAS~resolution, re-evaluate the best-fit global dust properties, and
fit addition parameters of the two-component model as a function of position
on the sky.

@@

The shape of the two-component spectrum we will consider is given by:

\begin{equation}
M_{\nu} \propto f_{1}q_{1}(\frac{\nu}{\nu_{0}})^{\beta_1}B_{\nu}(T_1) + (1-f_{1})q_{2}(\frac{\nu}{\nu_0})^{\beta_2}B_{\nu}(T_2)
\end{equation}

>>>>

The primary FDS99 analysis considered the grain properties, for example the
emissivity power law indices $\beta$, to be constant over the sky, and 
performed a correlation slope analysis to constrain these parameters with
FIRAS and DIRBE observations. A DIRBE 240$\mu$m/100$\mu$m ratio was constructed
to account for temperature variation at $\sim$1.3$^{\circ}$ resolution. In this
work we seek to apply FDS99-like emission models to the \PLANCK~data set, which
offers a dramatic enhancement in angular resolution relative to the FIRAS 
spectra. The \PLANCK~data allow us to derive a temperature correction at 
near-\IRAS~resolution, re-evaluate the best-fit global dust properties, and
fit additional parameters of the two-component model as a function of position
on the sky.

@@

The shape of the two-component model spectrum we will consider is given by:

\begin{equation}
M_{\nu} \propto f_{1}q_{1}\Big(\frac{\nu}{\nu_{0}}\Big)^{\beta_1}B_{\nu}(T_1) + (1-f_{1})q_{2}\Big(\frac{\nu}{\nu_0}\Big)^{\beta_2}B_{\nu}(T_2)
\end{equation}
